\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-08 manuscript/main.tex
new file:   analysis/placebo-test/.Rhistory 	new file:   analysis/placebo-test/conces_platform.dta 	new file:   figures/placebo_results/placebo_entry_concession.pdf 	new file:   figures/placebo_results/placebo_entry_lead.pdf 	new file:   figures/placebo_results/placebo_entry_num.pdf 	new file:   figures/placebo_results/placebo_entry_period.pdf 	new file:   figures/placebo_results/placebo_plat_concession.pdf 	new file:   figures/placebo_results/placebo_plat_lead.pdf 	new file:   figures/placebo_results/placebo_plat_num.pdf 	new file:   figures/placebo_results/placebo_plat_period.pdf 	deleted:

\documentclass[11pt]{article}
\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage{adjustbox}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm}
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{endnotes}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfig}
\pgfplotsset{compat=1.14}
\usepackage{longtable}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
\usepackage{authblk}
\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

@@

We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_entry}. For this test, we employed a neighborhood sample with randomly generated treatment effects. Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects. The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect (Continued)}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did_2.tex}

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_platform} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis.

@@

@@

\begin{table}[H]
  \caption{Other Meausre Indices of the Network Effect}
  \label{other:measures}
  \input{../result_tables/other_indices_appendix.tex}
\end{table}
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage{adjustbox}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm}
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{endnotes}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfig}
\pgfplotsset{compat=1.14}
\usepackage{subcaption}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
\usepackage{authblk}
\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

@@

We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}. For this test, we employed a neighborhood sample with randomly generated treatment effects. Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects. The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions. For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions. This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency. In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect}
      \label{tab:heter_platform_did_1}
      \input{../result_tables/heter_platform_did_1.tex}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect (Continued)}
      \label{tab:heter_platform_did_2}
      \input{../result_tables/heter_platform_did_2.tex}

@@

Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups. Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences. The treatment effect becomes significant only after the first period, aligning with our empirical findings. We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion. The test result also shows that there is no other confounding factors affecting our analysis.

@@

\section{Placebo Test}

\begin{figure}[ht]
  \centering
  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_num.pdf}\label{fig:placebo_num_entry}}
  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_lead.pdf}\label{fig:placebo_lead_entry}}
  \hfill % Adds horizontal space between figures
  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_period.pdf}\label{fig:placebo_period_entry}}
  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_concession.pdf}\label{fig:placebo_concession_entry}}
  \caption{Placebo Test to Entry Effect}
  \label{fig:placebo_test_entry}
\end{figure}

\begin{figure}[ht]
  \centering
  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_num.pdf}\label{fig:placebo_num_plat}}
  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_lead.pdf}\label{fig:placebo_lead_plat}}
  \hfill % Adds horizontal space between figures
  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_period.pdf}\label{fig:placebo_period_plat}}
  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_concession.pdf}\label{fig:placebo_concession_plat}}
  \caption{Placebo Test to Platform-Mediated Consolidation Effect}
  \label{fig:placebo_test_plat}
\end{figure}

@@

The results also indicate that the local network effect of Lianjia tends to be sparse and the network is not well-connected. The network effect is primarily characterized by local clustering, with moderate network strength.

\end{document}

\begin{table}[H]
  \caption{Other Meausre Indices of the Network Effect}
  \label{other:measures}
  \input{../result_tables/other_indices_appendix.tex}
\end{table}
